---
title: "Making pretty figures using MRIcrotome"
author: "Jason Lerch"
date: "`r Sys.Date()`"
---

Load the required data from a file; for the moment, this contains two 3D volumes; _anatVol_ and _stats_ containing the anatomy to use in the background and the output of some statistical computations.

```{r}
load("sliceData.RData")
```

The best way to use MRIcrotome is through pipes; let's load the full tidyverse for now (though only pipes are actively used). Also, the graphics subsystem is _grid_ graphics, so let's go ahead and load that as well.

```{r}
library(tidyverse)
library(grid)
library(MRIcrotome)
```

That's it for the set-up. On to actual package usage.

## Simple figures

Starting off with the simplest figure; a coronal slice through the brain.


```{r}
sliceSeries(nrow = 1, slices=200) %>% 
  anatomy(anatVol, low=700, high=1400) %>% 
  draw()
```

That's the basic anatomy of displaying MRI anatomy. It always begins with a call to sliceSeries, following by a call to anatomy, and finally the command to draw the results.

Let's prettify it, and overlay the stats.

```{r}
sliceSeries(nrow = 1, slices=200) %>% 
  anatomy(anatVol, low=700, high=1400) %>% 
  overlay(stats, low=2, high=6, symmetric = T) %>%
  draw()
```

So far, so good. A legend would be nice, though.

```{r}
sliceSeries(nrow = 1, begin=200, end=300) %>% 
  anatomy(anatVol, low=700, high=1400) %>% 
  overlay(stats, low=2, high=6, symmetric = T) %>%
  legend("t-statistics") %>%
  draw()
```

The command is called sliceSeries for a reason ...

```{r}
sliceSeries(nrow = 5, ncol=5, begin=100, end=350) %>% 
  anatomy(anatVol, low=700, high=1400) %>% 
  overlay(stats, low=2, high=6, symmetric = T) %>%
  legend("t-statistics") %>%
  draw()
```

You can also have more than one slice series:

```{r, fig.width=3, fig.height=6}
sliceSeries(nrow = 8, begin=100, end=350) %>% 
  anatomy(anatVol, low=700, high=1400) %>% 
  sliceSeries() %>% # if no arguments are specified, reuse previous sliceSeries args
  anatomy() %>% # if no arguments are specified, reuse previous anatomy call
  overlay(stats, low=2, high=6, symmetric = T) %>%
  legend("t-statistics") %>%
  draw()
```

And with some titles:

```{r, fig.width=3, fig.height=6}
sliceSeries(nrow = 8, begin=100, end=350) %>% 
  anatomy(anatVol, low=700, high=1400) %>% 
  addtitle("Anatomy") %>%
  sliceSeries() %>%
  anatomy() %>%
  overlay(stats, low=2, high=6, symmetric = T) %>%
  addtitle("Stats") %>%
  legend("t-statistics") %>%
  draw()
```

And change the layout orientation

```{r, fig.width=8, fig.height=2}
sliceSeries(ncol = 8, begin=100, end=350) %>% 
  anatomy(anatVol, low=700, high=1400) %>% 
  addtitle("Anatomy") %>%
  sliceSeries() %>%
  anatomy() %>%
  overlay(stats, low=2, high=6, symmetric = T) %>%
  addtitle("Stats") %>%
  legend("t-statistics") %>%
  draw(layout = "row")
```

Multiple legends

```{r, fig.width=8, fig.height=2}
sliceSeries(ncol = 8, begin=100, end=350) %>% 
  anatomy(anatVol, low=700, high=1400) %>% 
  addtitle("Anatomy") %>%
  legend() %>%
  sliceSeries() %>%
  anatomy() %>%
  overlay(stats, low=2, high=6, symmetric = T) %>%
  addtitle("Stats") %>%
  legend("t-statistics") %>%
  draw(layout = "row")
```

Let's do multiple legends on the same slice series, going with a column layout

**TODO: cannot use no-args version of anatomy() if asking for a legend**
```{r, fig.width=3, fig.height=6}
sliceSeries(nrow = 8, begin=100, end=350) %>% 
  anatomy(anatVol, low=700, high=1400) %>% 
  addtitle("Anatomy") %>%
  sliceSeries() %>%
  anatomy(anatVol, low=700, high=1400) %>%
  legend() %>%
  overlay(stats, low=2, high=6, symmetric = T) %>%
  addtitle("Stats") %>%
  legend("t-statistics") %>%
  draw()
```

It can also do contours

```{r}
sliceSeries(nrow = 1, begin=200, end=300) %>% 
  anatomy(anatVol, low=700, high=1400) %>% 
  contours(anatVol, levels=c(1000, 1400), col="blue") %>%
  draw()
```

Of course contours can be mixed with sliceSeries as you please

```{r}
sliceSeries(nrow = 1, begin=200, end=300) %>% 
  anatomy(anatVol, low=700, high=1400) %>% 
  sliceSeries() %>%
  anatomy() %>%
  contours(anatVol, levels=c(1000, 1400), col="blue") %>%
  sliceSeries() %>%
  contours(anatVol, levels=c(1000, 1400), col="blue") %>%
  draw()
```

Contours can be given different colours, linetypes, and widths

```{r}
sliceSeries(nrow = 1, begin=200, end=300) %>% 
  contours(anatVol, levels=c(1000, 1400), col=c("blue", "red"), lwd=1:2, lty=c(1,3)) %>%
  draw()
```

The most likely use is combined with stats - let's highlight the most significant:

```{r}
sliceSeries(nrow = 1, begin=200, end=300) %>% 
  anatomy(anatVol, low=700, high=1400) %>% 
  overlay(stats, low=2, high=6, symmetric = T) %>%
  legend("t-statistics") %>%
  contours(abs(stats), levels=c(3,5), lwd=2, lty=c(3,1), col="green") %>%
  draw()
```

Contours can of course have legends, too.

```{r}
sliceSeries(nrow = 1, begin=200, end=300) %>% 
  anatomy(anatVol, low=700, high=1400) %>% 
  overlay(stats, low=2, high=6, symmetric = T) %>%
  legend("t-statistics") %>%
  contours(abs(stats), levels=c(3,5), lwd=2, lty=c(3,1), col="green") %>%
  legend("Most sig.") %>%
  draw()
```

And contours can take on any colour scale

```{r}
sliceSeries(nrow = 1, begin=200, end=300) %>% 
  anatomy(anatVol, low=700, high=1400) %>% 
  contours(abs(stats), levels=2:6, col=topo.colors(255), lty=3) %>%
  legend("t statistics") %>%
  draw()
```

And of course works in slice series with multiple slices too

```{r}
sliceSeries(nrow=5, ncol=6, begin=70, end=400) %>%
  contours(anatVol, levels=c(1000, 1200, 1500), col=gray.colors(255)) %>%
  draw()
```

Opacity can be controlled with the alpha parameter to anatomy and overlay:

```{r}
sliceSeries(nrow=5, begin=150, end=250) %>%
  anatomy(anatVol, low=700, high=1400) %>%
  overlay(stats, 2, 6, symmetric = T, alpha=0.1) %>%
  addtitle("alpha=0.1") %>%
  sliceSeries() %>% anatomy() %>%
  overlay(stats, 2, 6, symmetric = T, alpha=0.5) %>%
  addtitle("alpha=0.5") %>%  
  sliceSeries() %>% anatomy() %>%
  overlay(stats, 2, 6, symmetric = T, alpha=0.9) %>%
  addtitle("alpha=0.9") %>%  
  draw()
```

**TODO: empty subsequent sliceSeries and anatomy calls bug out if a single slice (rather than begin and end) were specified**

